### 2019-03-22 4_implementation.tex
Run spell check.

One challenge in implementing Task Bench for such a wide variety of
systems is that the capabilities of the systems vary considerably. For
example, some systems are \emph{implicitly parallel}, and provide some
form of parallelism discovery from sequential programs, whereas others
are \emph{explicitly parallel} and require users to specify the
parallelism in the program. As a rule of thumb we aim for the Task
Bench implementations to be represenative of how actual applications
would be written in the respective systems. Places where the Task
Bench implementations may be unidiomatic are noted below.

@@

Our Task Bench implementation is straightforward: we create a chare
array for the task graph, with one chare for each column. Methods are
used to implement dependencies, and a task is executed as soon as its
dependecies are all available. Collectives are used to synchronize the
completion of the task graph execution.

@@

PaRSEC~\cite{PARSEC13} is a task-based programming system which
supports two distinct programming models: \emph{parameterized task
  graphs} (PTG) and \emph{sequential task flow} (STF). In the PTG
model, the program consists of an analytical function which describes
the expansion of the task graph. PTG is therefore a more limited
programming model, but can potentially provide better performance
because the graph description is amenable to static analysis and can
be pruned efficiently for horizontally scalable execution.

@@

Spark's programming model is based of \emph{functional parallelism}, a
generalization of the MapReduce programming
model~\cite{MapReduce04}. The core computational abstraction in Spark
are operators such as map, reduce, filter, join, etc. which by virtue
of being pure functions are trivially known to be
parallizable. Functions in Spark operate on \emph{resilient
  distributed datasets} (RDDs), which are globally-visible,
dynamically single-assignment data structures that cached in memory
and written to disk for durability. One of Spark's primary
optimizations therefore is the caching of RDDs to avoid unnecessary
disk traffic, resulting in substantial speedups over MapReduce.

@@

X10~\cite{X1005} is an explicitly parallel programming language for
place-based programming. The core features of X10 are \emph{places}
which represent distributed memories, a PGAS model where references to
remote objects can be held (but can only be deferenced on the local
place), asynchronous tasks, and a place-changing construct to move the
execution of a task to a remote place. X10 also supports a variety of
synchronization primitives.

>>>>

One challenge in implementing Task Bench for such a wide variety of
systems is that the capabilities of the systems vary considerably. For
example, some systems are \emph{implicitly parallel}, and provide some
form of parallelism discovery from sequential programs, whereas others
are \emph{explicitly parallel} and require users to specify the
parallelism in the program. As a rule of thumb we aim for the Task
Bench implementations to be representative of how actual applications
would be written in the respective systems. Places where the Task
Bench implementations may be unidiomatic are noted below.

@@

Our Task Bench implementation is straightforward: we create a chare
array for the task graph, with one chare for each column. Methods are
used to implement dependencies, and a task is executed as soon as its
dependencies are all available. Collectives are used to synchronize the
completion of the task graph execution.

@@

PaRSEC~\cite{PARSEC13} is a task-based programming system which
supports two distinct programming models: \emph{parameterized task
  graphs} (PTG) and \emph{sequential task flow} (STF). In the PTG
model, the program consists of an analytic function which describes
the expansion of the task graph. PTG is therefore a more limited
programming model, but can potentially provide better performance
because the graph description is amenable to static analysis and can
be pruned efficiently for horizontally scalable execution.

@@

Spark's programming model is based of \emph{functional parallelism}, a
generalization of the MapReduce programming
model~\cite{MapReduce04}. The core computational abstraction in Spark
are operators such as map, reduce, filter, join, etc. which by virtue
of being pure functions are trivially known to be
parallelizable. Functions in Spark operate on \emph{resilient
  distributed datasets} (RDDs), which are globally-visible,
dynamically single-assignment data structures that cached in memory
and written to disk for durability. One of Spark's primary
optimizations therefore is the caching of RDDs to avoid unnecessary
disk traffic, resulting in substantial speedups over MapReduce.

@@

X10~\cite{X1005} is an explicitly parallel programming language for
place-based programming. The core features of X10 are \emph{places}
which represent distributed memories, a PGAS model where references to
remote objects can be held (but can only be dereferenced on the local
place), asynchronous tasks, and a place-changing construct to move the
execution of a task to a remote place. X10 also supports a variety of
synchronization primitives.
